Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-11-01 article.hid2-ub-cicd.ppam24.tex
up style and rework article model

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}

\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and 
Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Gwennolé Chappron \inst{1}\orcidID{0009-0003-7588-3370} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}
\usepackage{cleveref}

@@

This paper is organized as follows: \cref{sec:kub-workflow} discusses KUB's current workflow, \cref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, \cref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

The Ktirio urban building workflow, see \cref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth,page=1]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\subsubsection{Vegetation Modeling}

Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:

\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}

This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. 
\Cref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

\Cref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in \cref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

\subsubsection{Conclusion on mesh construction}
Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.

@@

@@

@@

In \cref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in \cref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in \cref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in \cref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in \cref{fig:view-factor}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-devops.pdf}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see \cref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. 
The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing.
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

\Cref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++.
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-feelpp-hpcops.pdf}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth,page=1]{img-ub-devops-hpcops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications.
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

\Cref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

\Cref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\linewidth,page=2]{img-ub-devops-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}
\label{sec:benchmarking}

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance.
Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates.
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings).
The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see \cref{fig:kub-hpcops}.
\Cref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina.
They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in \cref{fig:execution-breakdown}. 
\cref{fig:execution-breakdown} reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}

@@

>>>>

\documentclass[runningheads]{llncs}
\usepackage{fullpage}
\usepackage{graphicx} % for including images
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage{wrapfig}
\usepackage[]{subcaption}
\usepackage{multicol}
\usepackage{url}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage{paralist}
\usepackage{amsmath}
\definecolor{darkred}{rgb}{0.6, 0, 0}
\definecolor{darkgreen}{rgb}{0, 0.5, 0}
\definecolor{darkblue}{rgb}{0, 0, 0.5}
\definecolor{darkmagenta}{rgb}{0.5, 0, 0.5}
\usepackage{hyperref}

@@

\title{Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems}
\author{Luca Berti\inst{1} \and Vincent Chabannes \inst{1}\orcidID{0009-0005-3602-3524} \and
Javier Cladellas \inst{1}\orcidID{0009-0003-8687-7881} \and 
Abdoulaye Diallo \inst{1}\orcidID{0009-0006-8731-0547}\ \and
Maryam Maslek Elayam \inst{1}\orcidID{0000-0003-0880-5180} \and
Philippe Pinçon \inst{1}\orcidID{0009-0009-7724-3055 } \and
Christophe Prud'homme\inst{1}\orcidID{0000-0003-2287-2961}}
\institute{Cemosis, IRMA UMR 7501, University of Strasbourg, CNRS\\ 
\email{\{vincent.chabannes,christophe.prudhomme\}@cemosis.fr}}
\date{\gitReln\  \gitAuthorDate\ (\gitAbbrevHash)}
\authorrunning{V. Chabannes et al.}

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}

@@

This paper is organized as follows: Section~\ref{sec:kub-workflow} discusses KUB's current workflow, Section~\ref{sec:urban-building} provides an overview of some modeling and simulation components, and finally, Section~\ref{sec:cicd-framework} delves into the CI/CD processes from standard DevOps to HPCops tailored for EuroHPC environments.

@@

The Ktirio urban building workflow, see Figure~\ref{fig:kub-workflow}, integrates various data sources and computational tools to simulate and analyze urban building energy and its impact on urban environments. The process encompasses data acquisition, processing, simulation, and analysis, eventually coupled with Urban Air Pollution (UAP) models.

\begin{figure}
    \centering
    \includegraphics[width=.9\textwidth]{img-kub-workflow.pdf}
    \caption{Current Urban Building Workflow from localization to city energy simulation report.}
    \label{fig:kub-workflow}
\end{figure}

@@

\subsubsection{Vegetation Modeling}
Including vegetation (trees) in our geometric model is essential for the simulation of buildings. The shading provided by trees and the cooling provided by wooded areas had a significant impacts on building environment  . We use the OpenStreetMap database to obtain the metadata associated with the vegetation. In addition to the position of the trees, we can also obtain other information, such as the tree's height and species. The current strategy is as follows:
\begin{itemize}
\item Definition of a reference tree library that lists a certain number of tree species at different levels of precision (LOD). These geometric entities are parameterized so that a transformation can be applied.
\item Fetching vegetation metadata via OpenStreetMap. The attributes (height, species) are not always available, so we try to define them as best as we can (by searching around).
\item Creating a tree geometric model using an affine transformation of the reference tree model.
\end{itemize}

\subsubsection{Integration of all urban geometric components}
This process involves creating a conforming mesh that includes all components (buildings, terrains, vegetation). Moreover, this step requires accomplishing some challenges by using complex geometric algorithms to realize the following points: \textit{(i)} Ensure that buildings on slopes are accurately modeled by adapting their height and embedding them into the terrain mesh. The figure~\ref{fig:city-grenoble-terrain} illustrates this aspect; \textit{(ii)} applies the intersection of buildings and consequently defines contact zones that can be included in building thermal models (coupling). \textit{(iii)} Apply the intersection of vegetation with buildings and terrain; and finally \textit{(iv)} Improve mesh quality after the previous geometric operations (mesh adaption).

@@

The figure~\ref{fig:partitioning} illustrates the different strategies discussed previously and presents a reconstruction of New York City in figure \ref{fig:city-ny-largescale}. This geometric model has an area of 400 $km^2$ (20 km square side of 20 km) and has generated around 450000 buildings. This example requires the large-scale approach discussed but not yet implemented or tested.

@@

\subsubsection{Conclusion on mesh construction}

Our strategy aims to improve the efficiency and scalability of the mesh generation process and enhance the fidelity and accuracy of the urban models used in simulations.

@@

\subsubsection{Heat transfer model in buildings}
\label{sec:heat-transfer-in-buildings}

The physical model of city buildings is based on a multizone model.
One zone is allocated per building floor. 
The energy balance for each zone is calculated by taking into account energy exchanges with adjacent zones and the environment.

The energy balance is written according to the first law of thermodynamics: in an isolated system, the sum of all forms of energy is constant.
\begin{equation}
    C \frac{dT}{dt} = \phi_{\mathrm{HVAC}} + \phi_{\mathrm{gain}} - \phi_{\mathrm{losses}}
\end{equation}
where
\begin{inparaenum}[\it (i)]
    \item $C \dfrac{dT}{dt}$ represents the thermal inertia of the construction, quantifying how the temperature of the zone changes over time due to its thermal mass. Specifically,
    $C$ is a measure of how much heat a material can store and release, combining the heat capacity of the construction (how much energy is required to change the temperature) with the rate of temperature change and 
    $\dfrac{dT}{dt}$ is the rate of change of temperature with respect to time. A higher thermal inertia means the construction will have a slower rate of temperature change in response to energy inputs and losses, effectively buffering temperature fluctuations;
    \item $\phi_{\mathrm{HVAC}}$ represents the energy input from the Heating, Ventilation, and Air Conditioning (HVAC) systems. It includes energy added to the zone to maintain desired temperature levels;
    \item $\phi_{\mathrm{gain}}$, referred to as free energy gain, includes solar gains (heat from sunlight) and internal gains (heat generated by occupants and equipment);
    \item $\phi_{\mathrm{losses}}$ represents the energy lost through walls, roofs, floors, and air exchanges with the environment.
\end{inparaenum}

\paragraph{HVAC heat flow} In the version of the model at the time of writing, the HVAC system is treated as an ideal heat source, which means it adjusts its output to maintain a set temperature within the building.

\paragraph{Heat gain} Heat gain is the addition of energy to the building, derived from two sources: \textbf{internal heat gains} and \textbf{solar heat gains}.

\paragraph{Internal heat gain} The internal heat gain captures the heat produced by occupants inside the building. 
It is modeled as a function of metabolic rate $\mathrm{Met}$ and the number of inhabitants, $d_i$, which varies over time $t$:
\begin{equation}
  \phi_{\mathrm{int}} = \mathrm{Met} \cdot d_i(t)
\end{equation}

\paragraph{Solar heat gain} The total solar heat gain includes contributions from direct, diffuse, and reflected solar radiation, taking into account the building’s surface characteristics and shading coefficient:
\begin{equation}
  \phi_{\mathrm{solar}} = \alpha \cdot S \cdot \left( E_{\mathrm{dir}} + E_{\mathrm{diff}} + E_{\mathrm{ref}} \right) \cdot S_C
\end{equation}
Direct solar radiation is the component of solar radiation adjusted for the angle of incidence of the sunlight:
\begin{equation}
  E_{\mathrm{dir}} = F_{\mathrm{dir}} \cdot \cos(I)
\end{equation}
Here, $F_{\mathrm{dir}}$ is the direct solar radiation, which is a function of the horizontal solar radiation measured by a weather station:
\begin{equation}
  F_{\mathrm{dir}} = \dfrac{F_{\mathrm{dir,Hz}}}{\sin(H_s)}
\end{equation}
The term $\cos(I)$ calculates the cosine of the angle of incidence of sunlight, incorporating the sun's altitude and azimuth angles as well as the building's tilt angle:
\begin{equation}
  \cos(I) = \cos(H_s) \cdot \sin(\beta) \cdot \cos(A_{zs} - A_z) + \sin(H_s) \cdot \cos(\beta)
\end{equation}
Diffuse solar radiation includes contributions from the sky dome and is adjusted for the building's tilt:
\begin{equation}
  E_{\mathrm{diff}} = F_{\mathrm{dif,Hz}} \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right)
\end{equation}
Reflected solar radiation is calculated using the total horizontal radiation and the environment's albedo:
\begin{equation}
  E_{\mathrm{ref}} = \left[ F_{\mathrm{dir,Hz}} + F_{\mathrm{dif,Hz}} \right] \cdot \left( \dfrac{1 + \cos(\beta)}{2} \right) \cdot \text{albedo}
\end{equation}

\paragraph{Conduction losses} Energy loss through walls is computed by summing the losses across all wall segments. It depends on the heat transfer coefficient, the wall area, and the temperature difference between the indoor and outdoor environments. In our current model, we simplify the calculations by not including the effects of thermal bridges, as they depend on specific information about the building's envelope, which we do not have:
\begin{equation}
  \phi_{\mathrm{wall}} = \sum_{j} U_j \cdot S_j \cdot \Delta T
\end{equation}
The convection losses are computed differently depending on the surface of the wall to which they are applied. On the interior surface, we apply a constant:
\begin{equation}
  \phi_{\mathrm{conv,int}} = \alpha_{\mathrm{conv}} \cdot \Delta T
\end{equation}
On the exterior surface, we use a forced convection model:
\begin{equation}
  \phi_{\mathrm{conv,ext}} = \left( 1.8 + 4.8 \cdot v_{\mathrm{air}} \right) \cdot \Delta T
\end{equation}

\paragraph{Radiation losses} Radiation losses describe the heat energy lost due to thermal radiation, impacting both energy efficiency and thermal comfort.
We differentiate between the exterior of the wall that exchanges with the sky and the interior where the walls exchange with each other.
namely, for the exterior radiation exchange:
\begin{equation}
  \phi_{\mathrm{net,sky}} = \varepsilon_i \cdot \sigma \cdot \left( T_i^4 - T_{\mathrm{sky}}^4 \right)
\end{equation}
and for the interior radiation exchange:
\begin{equation}
  J[i] = \varepsilon_i \cdot \sigma \cdot T_i^4 + \left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]
\end{equation}
where the radiative heat exchange $J[i]$ includes two terms:
\begin{inparaenum}[\it (i)]
    \item $\varepsilon_i \cdot \sigma \cdot T_i^4$, which calculates the heat radiated by surface $i$ where $\varepsilon_i$ measures how effectively the surface emits radiation and $T_i^4$ reflects that radiative heat loss increases rapidly with temperature; and
    \item $\left( 1.0 - \varepsilon_i \right) \cdot \sum_{j=1}^{n} F[i,j] \cdot J[j]$, which accounts for the heat absorbed from other surfaces $j$ within the zone. The factor $\left( 1.0 - \varepsilon_i \right)$ adjusts for the fraction of incoming radiation not emitted by surface $i$.
\end{inparaenum}
The net radiation flow is given by:
\begin{equation}
  \phi_{\mathrm{net,int}}[i] = S \cdot \dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)
\end{equation}
Net radiation flow $Q_{\mathrm{flow}}[i]$ considers:
\begin{inparaenum}[\it (i)]
    \item $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i} \cdot \left( \sigma \cdot T_i^4 - J[i] \right)$, which calculates the net heat flow due to radiation for surface $i$, considering the difference between the heat emitted by the surface and the heat received from other surfaces. The ratio $\dfrac{\varepsilon_i}{1.0 - \varepsilon_i}$ scales the net flow based on the emissivity of the surface.
\end{inparaenum}

\paragraph{Air change} This term represents the energy loss due to air exchange between the zone and the exterior:
\begin{equation}
  \phi_{\mathrm{air}} = 0.34 \cdot Q_v \cdot \Delta T
\end{equation}

The described thermal models are implemented using the Modelica language, which is an object-oriented, equation-based language well-suited for modeling complex physical systems. 
These models are then transformed into Functional Mock-up Units (FMUs) compliant with the Functional Mock-up Interface (FMI) standard. 
FMUs encapsulate the models and enable them to be shared and integrated across different simulation environments.

\paragraph{Conclusion}

By integrating these models within a high-performance computing framework, it is possible to simulate the thermal behavior of city-scale building clusters. This facilitates the assessment of energy consumption, thermal comfort, and the impact of various energy-saving strategies under different environmental conditions and operational scenarios.

@@

\subsubsection{Modelica for Multizone Heat Transfer}

The FMUs built from \cref{sec:heat-transfer-in-buildings} are loaded by the \texttt{Feel++} environment.

Input data for the models are sourced from available building information, such as geometric dimensions, material properties, and occupancy schedules.
When specific data are unavailable, default values are assigned based on the building's construction year, referencing standard building codes or typical practices from that period.
This approach ensures that the models can be applied to a wide range of buildings, even when detailed information is limited.

@@

In the figure~\ref{fig:solar-masks-vf}, we illustrate \textit{(i)} the solar masks of building face oriented eastwise for a discretization of the sun position in the panel~\ref{fig:sm-building-east}, \textit{(ii)} the solar masks for an entire building for discretization of the sun position in the panel~\ref{fig:sm-whole-building}, \textit{(iii)} a visualization of the solar mask early morning of the city center of Strasbourg in panel~\ref{fig:sm-strasbourg} and \textit{(iv)} an image of a standard benchmark~\cite{van_eck_surface_2016} for the computation of view-factors and solving the heat transfer problems between three building blocks in 2D subsequently in panel~\ref{fig:view-factor}.

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-devops.png}
    \caption{CI/CD DevOps for Feel++}
    \label{fig:feelpp-devops}
\end{figure}
The CI/CD workflow, see Figure~\ref{fig:feelpp-devops}, is crucial for efficiently integrating and deploying updates across all projects that utilize the Feel++ framework. The workflow leverages various main ingredients of GitHub Actions features.
\begin{enumerate}
    \item \textbf{Pull Requests and Merges:} Triggering CI to verify that new code integrations meet all tests and standards.
    \item \textbf{Graphical User Interface (GUI) thanks to \texttt{workflow\_dispatch}:} Enabling developers to manually trigger pipelines through a GUI, which facilitates rapid deployment or testing. 
    \item \textbf{Scheduled Runs:} Conducting regular updates and maintenance checks to ensure continuous system integrity and responsiveness.
\end{enumerate}

@@

Figure~\ref{fig:feelpp-hpcops} illustrates the HPC CI/CD or HPCOps workflow for Feel++. 
\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-compressed-feelpp-hpcops.png}
    \caption{CI/CD HPCOps for Feel++}
    \label{fig:feelpp-hpcops}
\end{figure}

@@

\begin{wrapfigure}{R}{.7\linewidth}
    \centering
    \includegraphics[width=\linewidth]{img-ub-devops.pdf}
    \caption{KUB standard DevOps}
    \label{fig:kub-devops}
\end{wrapfigure}
This framework leverages cutting-edge computational technologies, ensuring the high performance and accuracy of the Feel++ framework and Feel++-based applications. 
It sets a benchmark for integrating modern software frameworks with advanced HPC infrastructure to significantly advance computational research and applications.

Figure~\ref{fig:kub-devops} shows that the CI/CD standard DevOps framework for KUB uses similar steps.

Figure~\ref{fig:kub-hpcops} finally shows the HPCOps deployed on EuroHPC systems to check the parallel properties and correctness of the pilot on large-scale cases. It extends Feel++ HPC ops with additional steps to handle our complex pre- and post-processing steps.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{img-ub-hpcops.pdf}
    \caption{Ktirio Urban Building HPCOps workflow}
    \label{fig:kub-hpcops}
\end{figure}

\subsection{Benchmarking KUB}

Finally, we display some results of our benchmarking activities~\cite{hidalgo2_d31_2024} for the KUB application regarding HPC performance. Running these experiments regularly is essential for maintaining the program's efficiency when developing the application and after machine updates. 
Hence, we have used the KUB application in the Strasbourg city center, with a square area of $4 \mathrm{km}^2$ (approximately 17K buildings). The scalability results were realized on EuroHPC JU systems obtained with our HPCOps pipeline; see Figure~\ref{fig:kub-hpcops}. Figure \ref{fig:scalability} depicts the speedup achieved on Discoverer, Karolina, and MeluXina. They present results for the total execution (end-to-end) of the KUB application and the simulation component.

@@

To better understand what causes this degradation, we measure the computing times of the different stages of the pipeline and present the execution breakdown in Figure \ref{fig:execution-breakdown}. This figure reports the portion of the total execution taken by:
\begin{itemize}
\item Pre-processing (Pre-proc): The time elapsed in initialization before entering the time loop of the simulation
\item Simulation (Simulation): The cumulative time spent calculating the new solution at each time step
\item Post-processing (Post-proc): The cumulative time spent exporting results, i.e., generating files containing the output of the UB model.
\end{itemize}

@@

\textbf{Nomenclature}\\
\begin{multicols}{2}
$\alpha$ : Absorption of a material.\hfill[-]\\
$\alpha_{conv}$=10 : Heat conductance of convection.\hfill[-]\\
$\beta$ : Angle of inclination of the wall to the horizontal.\hfill[-]\\
$\Delta T$ : Temperature difference.\hfill[K]\\
$\epsilon$ : Emissivity of the surface.\hfill[-]\\
$\phi_{air}$ : Air heat flow.\hfill[W]\\
$\phi_{net}$ : Radiative heat flow.\hfill[W]\\
$\phi_{solar}$ : Solar heat flow from short wavelength.\hfill[W]\\
$\phi_{wall}$ : Heat flow through a wall.\hfill[W]\\
$\sigma$ : Stefan-Boltzmann constant $5,67\cdot10^{-8}$.\hfill[W$\cdot m^{-2}\cdot K^{-4}$]\\
$albedo$ : Reflective properties of the material.\hfill[-]\\
$A_z$ : Azimuth of the surface.\hfill[-]\\
$A_{zs}$ : Azimuth of the sun.\hfill[-]\\
$C$ : Heat capacity of the zone.\hfill[W$\cdot K^{-1}$]\\
$d_{inhabitant}(timetable)$ : Density of inhabitants as a function of the timetable set for the building type.\hfill[-]\\
$E_{dir}$ : Direct solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{diff}$ : Diffuse solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$E_{ref}$ : Reflected solar heat flow.\hfill[W$\cdot m^{-2}$]\\
$F_{dir}$ : Direct solar radiation.\hfill[W$\cdot m^{-2}$]\\
$F_{dir,Hz}$ : Direct solar radiation on a horizontal surface given by climate data.\hfill[W$\cdot m^{-2}$]\\
$F_{ij}$ : View factor between $surface_{(i)}$ and $surface_{(j)}$.\hfill[-]\\
$H_s$ : Angular height of the sun.\hfill[-]\\
$J$ : Radiosity of a surface.\hfill[W$\cdot m^{-2}$]\\
$Met$ : Metabolic rate.\hfill[W]\\
$0.34\cdot Q_v$ : Airflow as a fraction of the zone's volume per hour multiplied by the air volumetric heat capacity.\hfill[W$\cdot K^{-1}$]\\
$S$ : Surface area.\hfill[m$^2$]\\
$S_C$ : Shading coefficient $\in$ [0,1].\hfill[-]\\
$U_j$ : Conductance of a $wall_j$.\hfill[W$\cdot m^{-2}\cdot K^{-1}$]\\
$V_{air}$ : Wind speed.\hfill[m$\cdot s^{-1}$]
\end{multicols}
